Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline.

### 2017-04-28 draft/ms_v5.tex
Add Masayuki to author list

\author{Song Huang \altaffilmark{1,2}
        Alexie Leauthaud \altaffilmark{1,2},
        Ryoma Murata \altaffilmark{2, 4},
        James Bosch \altaffilmark{3},
        Paul Price \altaffilmark{3},
        Robert Lupton \altaffilmark{3},
        Rachel Mandelbaum \altaffilmark{5},
        Claire Lackner \altaffilmark{2},
        Steven Bickerton \altaffilmark{2},
        Satoshi Miyazaki \altaffilmark{6}, 
        Jean Coupon \altaffilmark{7},
        HSC Collaboration \altaffilmark{8}}
%% ------------------------------------------------------------------------------------ %%

@@

\altaffiltext{6}{SOKENDAI (The Graduate University for Advanced Studies), Mitaka,
    Tokyo, 181--8588, Japan}

\altaffiltext{7}{Department of Astronomy, University of Geneva, ch. d'\'Ecogia 16, 
    1290 Versoix, Switzerland}

\altaffiltext{8}{Other affiliations}

>>>>

\author{Song Huang \altaffilmark{1,2}
        Alexie Leauthaud \altaffilmark{1,2},
        Ryoma Murata \altaffilmark{2, 4},
        James Bosch \altaffilmark{3},
        Paul Price \altaffilmark{3},
        Robert Lupton \altaffilmark{3},
        Rachel Mandelbaum \altaffilmark{5},
        Claire Lackner \altaffilmark{2},
        Steven Bickerton \altaffilmark{2},
        Satoshi Miyazaki \altaffilmark{6,7}, 
        Jean Coupon \altaffilmark{8},
        Masayuki Tanaka \altaffilmark{6}
        }
%% ------------------------------------------------------------------------------------ %%

@@

\altaffiltext{6}{National Astronomical Observatory of Japan, 2--21--1 Osawa, Mitaka, 
     Tokyo 181--8588, Japan}

\altaffiltext{7}{SOKENDAI (The Graduate University for Advanced Studies), Mitaka,
    Tokyo, 181--8588, Japan}

\altaffiltext{8}{Department of Astronomy, University of Geneva, ch. d'\'Ecogia 16, 
    1290 Versoix, Switzerland}
